Python as a machine learning language: experiences from the scikit-learn project

### 2013-04-29 paper.tex
and it's open source, too

scikit-learn \citep{pedregosa2011} is a machine learning library
for the Python programming language,
intended to tie in with the set of numeric and scientific packages
centered around the NumPy and SciPy libraries
\Citep{vanderwalt2011, varoquaux2013scipy}.
It is a library, rather than a novel (domain-specific) programming language,
intended to be called from Python programs;
at present, it offers no command line interface or GUI.

>>>>

scikit-learn \citep{pedregosa2011} is an open source machine learning library
for the Python programming language,
intended to tie in with the set of numeric and scientific packages
centered around the NumPy and SciPy libraries
\Citep{vanderwalt2011, varoquaux2013scipy}.
It is a library, rather than a novel (domain-specific) programming language,
intended to be called from Python programs;
at present, it offers no command line interface or GUI.
